Data preparation

### 2024-02-23 procesamiento/02-prod_prep-macro.Rmd
update ratios

names(wid_df)
# summary(wid_df)
wid_df <- 
wid_df %>% 
  select(country=country.x,year=year.x,country_yr,starts_with("wid_"))

wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")
wid_df <- wid_df %>% filter(year==2018)%>% select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_gini_disp) 
```

>>>>

names(wid_df)
# summary(wid_df)
wid_df <- 
wid_df %>% 
  dplyr::select(country=country.x,year=year.x,country_yr,starts_with("wid_"))

wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")
wid_df <- wid_df %>% filter(year==2018)%>% dplyr::select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_sd10d01,wid_gini_disp)

cor(wid_df)
```
